\documentclass[11.5pt]{moderncv}

\usepackage{setspace}
\usepackage{amssymb}
\usepackage{amsfonts}
\usepackage{amsmath}

\moderncvtheme[blue]{classic}

\usepackage[utf8] {inputenc}

\usepackage{amsmath}

\usepackage[scale = 0.93]{geometry}
\setlength{\hintscolumnwidth} {2.35 cm}
\AtBeginDocument{\recomputelengths}

\firstname{Peter}
\familyname{Seger}
\mobile{503.544.6599}
\email{peterhseger@gmail.com}
\homepage{peterhenryseger.com}

\nopagenumbers{}
\begin{document}
\maketitle

\vspace{-.3in}

\section{Education}

\cventry{2016 - Present
Class of 2020
}
{Franklin W. Olin College of Engineering}{}{Needham, MA}{}
{
	\textbf{Candidate for BSE in Computer Engineering.}
	  Coursework includes:
    Modeling and Simulation of The Real World;
    Design Nature;
    Introduction to Sensors, Instrumentation, and Measurement;
    Software Design*;
    Qualitative Engineering Analysis*
       (*denotes currently enrolled)
	\newline
	\textit{Recipient of 4-year, 50\% Olin Merit Scholarship.}
}

\cventry{2012 - 2016
GPA: 3.82}{Valley Catholic High School}{}{Beaverton, OR}{}
{
	AP National Scholar with Honors; English \& French National Honor Society.
	\begin{flushright}
	\vspace {-0.3 in}
	\end{flushright}
	\vspace {-0.1 in}
}

\section{Experience}
\vspace{0.05 in}

\cventry{2014-Present}
{Sound Engineer}
{Freelance}
{Portland, OR}
{}
{Self taught in the practice of live sound engineering including choosing equipment, setting it up, and running advanced shows. Engineered at music festivals, theatrical productions, and musicals including troubleshooting and organizing sound arrays. Installed fulls sound systems including equipment, software, and training. Worked as sound designer for the stage production of Dead Man's Cell Phone at Babson College. (Fall 2016)}

\cventry{2014-Present }
{Photographer}
{Peter Seger Photography}
{Portland, OR}
{}
{Work freelance with focuses in portrait, landscape, and sports photography. Grew business to a profitable level.
 Published in editorial articles in The Oregonian covering a Fun Run. Portfolio at \href{www.petersegerphotography.com}{petersegerphotography.com}}

\cventry{Summer 2014-2016}
{Head Counselor}
{Trollbacken Swedish Language and Culture Camp}
{Portland, OR}
{}
{Responsible for cabin of 10 boys aged 7-13. Head counselor responsibilities included leading activities and organizing staff. Worked alongside teaching staff to ensure the week went off without a hitch.}

\cventry{September 2016-Present}
{Library Assistant}
{Olin College of Engineering}
{Needham, MA}
{}
{Work to install and maintain new shelving system including new database. Worked to design and manufacture a facade for the student run coffee shop on campus.}

\vspace{0.05 in}
\section{Projects}

\cventry{Fall 2016}
{Wanderer}
{MIT Media Lab Reality Virtually AR/VR Hackathon}
{}
{}
{Worked in a team of five to create a VR experience for people with anxiety. Went in with no previous experience in Javascript, C\#, or Unity and created a bubbler feature using the newly release Good Daydream API to utilize the wand. More information can be found at \href{https://devpost.com/software/wanderers}{devpost.com/software/wanderers}}

\cventry{Fall 2016 -Present}
{Formula SAE}
{Olin College}
{}
{}
{Working to design and build the car's dashboard module which displays important driver data through the use of micro controllers. Interfaces with the data logging system to record useful driver data. Designed custom PCBs in Altium Designer then proceeded to place components and program the boards using C.}

\cventry{Fall 2016 -Present}
{SLAC (Stay Late and Create)}
{Olin College}
{}
{}
{Part of the leadership team for the club which promotes a collaborative work space to foster Olin's project based learning by holding Wednesday night meetings with snacks, student-led workshops, and corporate-led workshops. Worked to promote the club by creating a branded Facebook page, Instagram, and weekly email newsletter in HTML. Work with the leadership team to organize SLACfest, a festival of creativity during the spring semester which features an entire day of workshops, activities, and food. Work closely with corporate sponsors to gather funding and organize exciting  workshops for students.}

\section{Skills}

\cvline{}
{
Java,
Python,
HTML,
MatLab,
Altium Designer,
Solidworks,
3dsMax
Unity Engine,
Adobe Creative Suite,
Lightroom,
Microsoft Suite,
Apple Logic,
ProTools,
\LaTeX{},
laser cutter,
mill,
lathe.
}
\cvline{}
{Other: French language fluency \& conversational Swedish}

\end{document}